draft_yma

### 2021-12-14 draft_yma.Rmd
change the backward bu hand

```{r}
# No docs
step1 = update(full_fit, . ~ . -pdocs_1000)
summary(step1)

@@

mult.fit.final = lm(formula = crm_1000 ~ pop + pop18 + hsgrad + bagrad + poverty + 
    pcincome + region + pbeds_1000 + density_pop, data = cdi_model)
summary(mult.fit.final)
```

>>>>

```{r}
# No docs
step1 = update(trans_fit, . ~ . -pdocs_1000)
summary(step1)

@@

step4 = update(step3, . ~ . -hsgrad)
summary(step4)

mult.fit.final = lm(crm_1000^0.5 ~ pop + pop18 + bagrad + poverty + 
    pcincome + region + pbeds_1000 + density_pop, data = cdi_model)
summary(mult.fit.final)
```
